modelStudio - perks and features

### 2020-09-10 inst/doc/ms-perks-features.Rmd
version 2.0.0

`modelStudio::modelStudio` computes various (instance and dataset level) model explanations and produces
an interactive, customisable dashboard. It consists of multiple panels for plots with their short descriptions.
Easily save and share the HTML dashboard with others. Tools for model exploration unite with tools for
EDA (Exploratory Data Analysis) to give a broad overview of the model behavior.

@@

`N` is a number of observations used for calculation of
[Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles. 
`10*N` is a number of observations used for calculation of
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
`B` is a number of permutation rounds used for calculation of
[Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
Decrease `N` and `B` parameters to lower the computation time or increase
them to get more accurate empirical results.

@@

Change `viewer` parameter to set where to display `modelStudio`.
Best described in `r2d3` documentation:
[`r2d3 viewer argument`](https://rstudio.github.io/r2d3/articles/visualization_options.html#viewer).

@@

All options can be set outside of function call.
More on that [here](https://github.com/berndbischl/parallelMap#being-lazy-configuration).

@@

Customize some of `modelStudio` looks by overwriting default options returned
by the `ms_options()` function. Full list of options:
[documentation](http://modelstudio.drwhy.ai/reference/ms_options.html).

@@

@@

Use `explain_*()` functions from the [DALEXtra](https://github.com/ModelOriented/DALEXtra)
package to explain various models. Bellow basic example of making `modelStudio` for
a `mlr` model using `explain_mlr()`.

@@

* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain and Examine Predictive Models.](https://pbiecek.github.io/ema)
* The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)
* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence plots
are implemented in [ingredients](https://modeloriented.github.io/ingredients/)
* Break Down and Shapley Values plots are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)

>>>>

The `modelStudio()` function computes various (instance and dataset level) model explanations 
and produces a customisable dashboard, which consists of multiple panels for plots with their
short descriptions. Easily save the dashboard and share it with others. Tools for
[Explanatory Model Analysis](https://pbiecek.github.io/ema/) unite with tools for Exploratory Data Analysis 
to give a broad overview of the model behavior.

@@

- `N` is a number of observations used for calculation of
[Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles. 
- `10*N` is a number of observations used for calculation of
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
- `B` is a number of permutation rounds used for calculation of
[Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).

Decrease `N` and `B` parameters to lower the computation time or increase
them to get more accurate empirical results.

@@

Change `viewer` parameter to set where to display `modelStudio`.
[Best described in `r2d3` documentation](https://rstudio.github.io/r2d3/articles/visualization_options.html#viewer).

@@

All options can be set outside of the function call.
[How to use parallelMap](https://github.com/mlr-org/parallelMap#being-lazy-configuration).

@@

Customize some of the `modelStudio` looks by overwriting default options returned
by the `ms_options()` function.
[Full list of options](https://modelstudio.drwhy.ai/reference/ms_options.html).

@@

## Shiny

Use the `widget_id` argument and `r2d3` package to render the `modelStudio` output in Shiny.
See [Using r2d3 with Shiny](https://rstudio.github.io/r2d3/articles/shiny.html) and consider 
the following example:

```{r eval = FALSE}
library(shiny)
library(r2d3)

ui <- fluidPage(
  textInput("text", h3("Text input"), 
            value = "Enter text..."),
  uiOutput('dashboard')
)

server <- function(input, output) {
  #:# id of div where modelStudio will appear
  WIDGET_ID = 'MODELSTUDIO'

  #:# create modelStudio 
  library(modelStudio)
  library(DALEX)
  model <- glm(survived ~., data = titanic_imputed, family = "binomial")
  explainer <- explain(model,
                       data = titanic_imputed,
                       y = titanic_imputed$survived,
                       label = "Titanic GLM",
                       verbose = FALSE)
  ms <- modelStudio(explainer,
                    widget_id = WIDGET_ID,  #:# use the widget_id 
                    show_info = FALSE)    
  ms$elementId <- NULL                      #:# remove elementId to stop the warning

  #:# basic render d3 output
  output[[WIDGET_ID]] <- renderD3({
    ms
  })

  #:# use render ui to set proper width and height
  output$dashboard <- renderUI({
    d3Output(WIDGET_ID, width=ms$width, height=ms$height)
  })
}

shinyApp(ui = ui, server = server)
```

@@

Use `explain_*()` functions from the [DALEXtra](https://github.com/ModelOriented/DALEXtra/)
package to explain various models.

Bellow basic example of making `modelStudio` for a `mlr` model using `explain_mlr()`.

@@

* Theoretical introduction to the plots: [Explanatory Model Analysis. Explore, Explain and Examine Predictive Models.](https://pbiecek.github.io/ema/)
* The input object is implemented in [DALEX](https://modeloriented.github.io/DALEX/)
* Feature Importance, Ceteris Paribus, Partial Dependence and Accumulated Dependence explanations
are implemented in [ingredients](https://modeloriented.github.io/ingredients/)
* Break Down and Shapley Values explanations are implemented in [iBreakDown](https://modeloriented.github.io/iBreakDown/)
